---
title: "Ruoyu Zhang's PS07"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(leaflet)
library(sf)
library(maps)

# USA specific data
library(USAboundaries)
library(tidycensus)
library(tmaptools)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Introduction


I am Ruoyu (she/her), an undergrad studying 
*psychology & study of women and gender (swg)*
at Smith College. 
I am taking 
**Intro to statistics and data science** this semester. 
I use:    
*R   
*Python   
Below is an example of my coursework.


## Plots


```{r trip, echo=FALSE}

USA_map <-  maps::map("state", plot = FALSE, fill = TRUE)


# Convert maps package map object to sf object using st_as_sf() again:
USA_sf <- USA_map %>% 
  st_as_sf(crs = 4326)


trip <- tibble(
  name = c("UCSD", "Disneyland Park", "Universal Studios Hollywood"), 
  lat = c(32.8752631656,  33.812511, 34.141354), 
  lon = c(-117.236132389, -117.918976, -118.352898)
)

trip_sf <- trip %>%
  st_as_sf(coords = c("lon", "lat"), crs = 4326)


USA_map <-  maps::map("state", plot = FALSE, fill = TRUE)

USA_sf <- USA_map %>% 
  st_as_sf(crs = 4326)

CA_sf <- USA_sf %>%
  filter(ID == 'california')

ggplot() + geom_sf(data = CA_sf) +
  geom_sf(data = trip_sf,aes(col = name), size = 2) +labs(title = 'Trip coordinates in winter recess' )
  
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
